---
title: "sigurd version"
author: "Sigurd Fyhn Sørensen"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# START SPIVEY DATA 

## Packages
```{r}
pacman::p_load(readbulk)
pacman::p_load(MASS,lme4,GGally,ggpubr, reshape, boot)
pacman::p_load(ellipse, tidyverse, Hmisc)
pacman::p_load(pROC, devtools, reshape2, mousetrap)
pacman::p_load(lmerTest)
```


```{r}
spivey_df <- read_bulk("../Our_data/", extension = "csv")

```

## Load data 
```{r}
spivey_df_short <- spivey_df %>% 
  dplyr::select(left_stimuli_1, right_stimuli_1, timestamps_mouse, sound, practice, timestamps_mouse, xpos_mouse, ypos_mouse, response, response_time, count_trial_sequence, correct_response, correct, subject_nr, trial_type, live_row )

#write_csv(spivey_df_short, "mouse_spivey_short.csv")

spivey_df_short <- spivey_df_short %>% 
  filter(practice != "yes")
```


```{r}
t_test_accuracy <- spivey_df_short %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(subject_accuracy = 1-sum(correct)/n())
```
```{r}
t_test_accuracy_wide <- pivot_wider(t_test_accuracy, names_from = trial_type, values_from = subject_accuracy)
t_test_accuracy %>% 
  group_by(trial_type) %>% 
  dplyr::summarise(mean = mean(subject_accuracy))
```


```{r}
t.test(t_test_accuracy_wide$cohort, t_test_accuracy_wide$control, paired = TRUE)

```
```{r}
#model_accuracy <- lmerTest::lmer(correct~trial_type + (1|subject_nr), data = spivey_df_short)
#summary(model_accuracy)
```

```{r}
spivey_df_filter <- spivey_df_short %>% 
  filter(correct == 1)
```

```{r}
t_test_response_time <- spivey_df_filter %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(mean_response_time = mean(response_time))

t_test_response_time_wide <- pivot_wider(t_test_response_time, names_from = trial_type, values_from = mean_response_time)

t.test(t_test_response_time_wide$control, t_test_response_time_wide$cohort, paired = TRUE, alternative = "two.sided")
```
```{r}
mean(t_test_response_time_wide$cohort)
```

```{r}
mean(t_test_response_time_wide$control)
```


```{r}
model_response_time <- lmerTest::lmer(response_time~trial_type + (1|subject_nr), data = spivey_df_filter)
summary(model_response_time)
```





```{r}
#Subset for Accuracy == TRUE.
spivey_df_short_correct <- subset(spivey_df_short, correct == 1)
spivey_df_shot_correct <- subset(spivey_df_short_correct, practice == "no")

#TUrn Subject into factor
spivey_df_short_correct$subject_nr <- factor(spivey_df_short_correct$subject_nr)
```

# Mousetrap
```{r}
#creating mouse_trap object, extracting initiation times and creating a dataframe with only the relevant information
m <- mt_import_mousetrap(spivey_df_short_correct)

m_measures <- mt_measures(m)

data_initiation_time <- data.frame(subject_nr = spivey_df_short_correct$subject_nr, trial_type = spivey_df_short_correct$trial_type, initiation_time = m_measures$measures$initiation_time)
```

```{r}
head(data_initiation_time)
```


```{r}
t_test_initiation_time <- data_initiation_time %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(mean_initiation_time = mean(initiation_time))

t_test_initiation_time_wide <- pivot_wider(t_test_initiation_time, names_from = trial_type, values_from = mean_initiation_time)

t.test(t_test_initiation_time_wide$control, t_test_initiation_time_wide$cohort, paired = TRUE, alternative = "two.sided")
```
```{r}
mean(t_test_initiation_time_wide$control)
```
```{r}
mean(t_test_initiation_time_wide$cohort)
```


```{r}
model_initiation_time <- lmerTest::lmer(initiation_time~trial_type + (1|subject_nr), data = data_initiation_time)
summary(model_initiation_time)
```

```{r}
data_duration_time <- data.frame(subject_nr = spivey_df_short_correct$subject_nr, trial_type = spivey_df_short_correct$trial_type, duration_time = spivey_df_short_correct$response_time - m_measures$measures$initiation_time, response_time = spivey_df_short_correct$response_time, initiation_time = m_measures$measures$initiation_time)
```

```{r}
head(data_duration_time)
```
```{r}
t_test_duration_time <- data_duration_time %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(mean_duration_time = mean(duration_time))

t_test_duration_time_wide <- pivot_wider(t_test_duration_time, names_from = trial_type, values_from = mean_duration_time)

t.test(t_test_duration_time_wide$control, t_test_duration_time_wide$cohort, paired = TRUE, alternative = "two.sided")
```

```{r}
mean(t_test_duration_time_wide$control)
```
```{r}
mean(t_test_duration_time_wide$cohort)
```


```{r}
model_duration_time <- lmerTest::lmer(duration_time~trial_type + (1|subject_nr), data = data_duration_time)
summary(model_duration_time)
```


```{r}
m <- mt_import_mousetrap(spivey_df_short_correct)

#remap
m <- mt_remap_symmetric(m, use = 'trajectories', remap_xpos = "right", remap_ypos = "up")

m <- mt_exclude_initiation(m)
m <- mt_time_normalize(m, nsteps = 101, save_as = "tn_trajectories") #creates tn_trajectories

#Final prep of data.
#Make the end and start point together. 
m <- mt_align(m, use = "tn_trajectories", save_as = "tn_align_trajec", dimensions = c("xpos", "ypos"), coordinates = "isotropic", align_start = TRUE , align_end = TRUE, align_side = "right", verbose = FALSE)

m <- mt_scale_trajectories(m, use = "tn_align_trajec", save_as = "final_trajec", c("xpos", "ypos"), center = TRUE, scale = TRUE, within_trajectory = FALSE, prefix = "z_", transform = NULL)

m <- mt_measures(m, use = 'tn_trajectories')
```

```{r}
avg_trajec <- mt_plot_aggregate(m, use = "tn_align_trajec", color = "trial_type") +
  labs(title = "Averaged trajectories for each trial type", x = "X-position", y = "Y-position", colour = "Trial type") + theme(legend.position = c(0.8, 0.1), legend.direction = "horizontal")

```

```{r}
ggsave("Avg_trajec.png", plot = avg_trajec)
```


'''Different methods have been suggested for assessing the bimodality of mouse-tracking measure
distributions, each of which has advantages and disadvantages (see Freeman & Dale, 2013).

Hehman et al. (2015) focus on two specific methods (bimodality coefficient and Hartigan’s dip
statistic) which are implemented here.

If methods include BC, the bimodality coefficient is calculated using the bimodality_coefficient
function in this package. According to Freeman and Ambady (2010), a distribution is considered
bimodal if BC > 0.555.

Note that MouseTracker (Freeman & Ambady, 2010) standardizes variables within each subject
before computing the BC. This is also possible here using mt_standardize (see Examples).

If methods include HDS, Hartigan’s dip statistic is calculated using the dip.test function of the
diptest package. The corresponding p value (computed via linear interpolation) is returned.

If methods include HDS_sim, Hartigan’s dip statistic is calculated using the dip.test function with
the additional argument simulate.p.values=TRUE. In this case, the p value is computed from a
Monte Carlo simulation of a uniform distribution with B (default: 2000) replicates.'''



```{r}
#for "degree of curvature" Spivey standardises based on only subject_nr
#I do not calculate "degree of curvature" but use "average deviation from direct path" instead

#mt_check_bimodality(m, use_variables=c("MAD", "AD"), methods = c("BC", "HDS"), grouping_variables="trial_type")
#mt_example <- mt_standardize(m, use_variables=c("MAD", "AD"), within="subject_nr")

m_standardised_subject_nr <- mt_standardize(m,use_variables=c("AD"), within=c("subject_nr"), prefix="z_")
mt_check_bimodality(m_standardised_subject_nr, use_variables=c("z_AD"), methods = c("BC"), grouping_variables="trial_type")
```


```{r}
#distributions of average deviation
data.frame(z_AD = m_standardised_subject_nr$measures$z_AD, trial_type = spivey_df_short_correct$trial_type) %>% 
  ggplot(aes(x = z_AD, fill = trial_type)) +
  geom_histogram(alpha = 0.5, position = "identity")
```
```{r}
df_zAD <- data.frame(z_AD = m_standardised_subject_nr$measures$z_AD, trial_type = spivey_df_short_correct$trial_type) 

df_zAD %>% 
  group_by(trial_type) %>%
  dplyr::summarise(mean(z_AD), variance = var(z_AD))
```

```{r}
#if Spivey actually just means AUC when talking about "degree of curvature" then the following could be used
m_standardised_subject_nr <- mt_standardize(m,use_variables=c("AUC"), within=c("subject_nr"), prefix="z_")
mt_check_bimodality(m_standardised_subject_nr, use_variables=c("z_AUC"), methods = c("BC"), grouping_variables="trial_type")
```

```{r}
df_zAUC <- data.frame(z_AUC = m_standardised_subject_nr$measures$z_AUC, trial_type = spivey_df_short_correct$trial_type) 

df_zAUC %>% 
  group_by(trial_type) %>%
  dplyr::summarise(mean = mean(z_AUC), variance = var(z_AUC))
```


```{r}
#for "area under trajectory" Spivey standardises based on subject_nr and trial_type

#mt_check_bimodality(m, use_variables=c("MAD", "AD"), methods = c("BC", "HDS"), grouping_variables="trial_type")
#mt_example <- mt_standardize(m, use_variables=c("MAD", "AD"), within="subject_nr")

m_standardised_subject_nr <- mt_standardize(m,use_variables=c("AUC"), within=c("subject_nr", "trial_type"), prefix="z_")

#if "degree of curvatur" actually just is "area under the curve" then the following would be the bimodality coefficient
mt_check_bimodality(m_standardised_subject_nr, use_variables=c("z_AUC"), methods = c("BC"), grouping_variables="trial_type")
```

```{r}
df_zAUC <- data.frame(z_AUC = m_standardised_subject_nr$measures$z_AUC, trial_type = spivey_df_short_correct$trial_type) 

df_zAUC %>% 
  group_by(trial_type) %>%
  dplyr::summarise(mean = mean(z_AUC), variance = var(z_AUC))

```
```{r}
df_zAUC%>% 
  ggplot(aes(x = z_AUC, fill = trial_type)) +
  geom_histogram(alpha = 0.5, position = "identity")
```


```{r}
ks.test(filter(df_zAUC, trial_type == "control")$z_AUC, filter(df_zAUC, trial_type == "cohort")$z_AUC)
```


